String Constraints with Regex-Counting and String-Length Solved More Efficiently

### 2024-05-15 2024-5-13/setta2023_report/setta2023_report.tex
commit the paper extended by setta2023

\documentclass[landscape]{beamer}
\usepackage{xcolor}
\usepackage{amsmath, amsthm}
\newtheorem{benchmark}{Benchmark}
\newtheorem{environment}{Environment}
\newtheorem{distribution}{The Distribution of Counting Operators in Our Benchmark}
\usepackage{mathrsfs}
\usepackage{hyperref}
\usepackage{algpseudocode}
\usepackage{tikz}
\usetikzlibrary {decorations.pathmorphing, curvilinear, shadows,shapes.symbols, automata, positioning, shapes,arrows, matrix}
\usepackage{multicol}
\usepackage{pgfplots}
\usepackage{array}
\usepackage{colortbl}
\definecolor{grayshade}{gray}{0.9}
\usepackage{listings}
\lstdefinestyle{myjs}{
  language=C,
  basicstyle=\ttfamily,
  keywordstyle=\color{blue},
  stringstyle=\color{red},
  commentstyle=\color{green},
  backgroundcolor=\color{gray!10},
  breaklines=true,
  frame=single,
  captionpos=b
}
\usepackage{booktabs}
\usepackage{siunitx}

\linespread{1.5}
\newcommand{\aut}{\mathcal{A}}
\newcommand{\myvec}[1]{\overrightarrow{#1}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\anivar}{\mathfrak{x}}
\newcommand*{\ostrichrecl}{\rm OSTRICH^{RECL}}

@@

\title{String Constraints with Regex-Counting and
String-Length Solved More Efficiently}
\author{\textbf{Denghang Hu}, Zhilin Wu}
\institute{Institute of Software, University of Chinese Academy of Sciences}

@@

\begin{frame}{String is Important}
  \textbf{String is a primitive data type in program languages:}
  \begin{itemize}
    \item C/++/\#
    \item Java
    \item JavaScript/TypeScript
    \item Python
    \item Go
    \item ...
  \end{itemize}
\end{frame}

\begin{frame}{String is Widely Used in Security-Critical Situations}
  \begin{itemize}
    \item Input sanitisation, validation
    \item Quary generation for databases
    \item Data handling: XML, JSON, HTML
    \item Dynamic code generation
    \item ...
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{String is Error-Prone}
  \begin{tikzpicture}
    \node[starburst,drop shadow,fill=white,draw] at (0,0) {XSS Attack};
    \node[starburst,drop shadow,fill=white,draw] at (5,0) {ReDos Attack};
    \node[starburst,drop shadow,fill=white,draw] at (0,-3) {Broken Access Control};
    \node[starburst,drop shadow,fill=white,draw] at (5,-3) {...};
  \end{tikzpicture}
\end{frame}

\begin{frame}[fragile]{Detect Attacks by String Constraints}
  \textbf{Malicious User Input:}
  \begin{lstlisting}[style=myjs]
      <script> XSSAtack </script>
    \end{lstlisting}
  \textbf{Security String Constraints:}
  \begin{lstlisting}[style=myjs]
    (assert (not (str.contains x '<script>')))
  \end{lstlisting}
\end{frame}

\begin{frame}
  \frametitle{String Solvers}
  \begin{multicols}{2}
    \begin{itemize}
      \item ABC
      \item CVC3/4/5
      \item Gecode+S
      \item OSTRICH
      \item Stranger
      \item S3/p/\#
      \item Sloth
      \item SLENT
      \item TRAU/+
      \item Woorpje
      \item Z3str2/3/4/RE/Seq
      \item ...
    \end{itemize}
  \end{multicols}
\end{frame}

\begin{frame}{But...}
  \textbf{Existing Solvers Cannot Solve:}
  \begin{tikzpicture}
    \node (formula) at (0,0) {
      $
        x\in (\Sigma / a)^{\{1,60\}}(\Sigma / b)^{\{1,60\}}(\Sigma / c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120
      $
    };
    \node [rotate=45, scale=2, text=red!60, fill=yellow!20,draw,decorate,decoration={bumps,mirror}, opacity=0] at (1,0) {300s TIMEOUT};
  \end{tikzpicture}
\end{frame}
\begin{frame}{But...}
  \textbf{Existing Solvers Cannot Solve:}
  \begin{tikzpicture}
    \node (formula) at (0,0) {
      $
        x\in (\Sigma / a)^{\{1,60\}}(\Sigma / b)^{\{1,60\}}(\Sigma / c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120
      $
    };
    \node [rotate=45, scale=2, text=red!60, fill=yellow!20,draw,decorate,decoration={bumps,mirror}] at (1,0) {300s TIMEOUT};
  \end{tikzpicture}
\end{frame}

\begin{frame}[fragile]
  \frametitle{However ...}
  \textbf{Regex-Countings are Widely Used}
  \begin{table}
    \centering
    \begin{tabular}{l l l S[table-format=1.2]}
      \toprule
      \textbf{Rank} & \textbf{Type}  & \textbf{Example} & \textbf{\% Projects} \\
      \midrule
      1             & $\cdot\{1,\}$  & $z^+$            & 0.1                  \\
      3             & $\cdot\{0,\}$  & $z^*$            & 0.2                  \\
      18            & $\cdot\{n\}$   & $z\{8\}$         & 0.05                 \\
      20            & $\cdot\{n,m\}$ & $z\{8,9\}$       & 0.3                  \\
      \bottomrule
    \end{tabular}
    \caption{The Rank and Percentage of Regex-Countings in Python \footnote{Chapman,C. et al: Exploring regular expression usage and context in python}}
  \end{table}

@@

% Technical details : (8min)
% 1 What is Regex-Counting
% 2 normal ways (z3, cvc5, trau)
% 3 our ways
%   1 An example (5-7 pages)
%   2 Decisino procedure 1 pages
\section{Our Approach}
\begin{frame}{Example}
  \begin{tikzpicture}
    \node (placeholder) at (0,0) {
      $
        x\in (\Sigma / a)^{\{1,60\}}(\Sigma / b)^{\{1,60\}}(\Sigma / c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120
      $
    };
    \node [rotate=45, scale=2, text=red!60, fill=yellow!20,draw,decorate,decoration={bumps,mirror}, opacity=0] at (1,0) {300s TIMEOUT};
  \end{tikzpicture}
\end{frame}

\begin{frame}{Exsiting Techniques to Such Constraints}
  \begin{tikzpicture}
    \node [anchor=north, anchor=west, align=left, text width = \linewidth] (text) at (-3,0) {
      Rule-based (CVC5, Z3): \textbf{Repeatly unroll} counting operators by derivation rules. For example,
      $x\in \Sigma\cdot z \wedge z\in \Sigma^*c^+$ is derived from $x\in \Sigma^*c^+$ in CVC5.
    };
    \node (cvc5) at (0,-3) {
      \includegraphics[width=0.4\linewidth]{cvc5_logo.png}
    };
    \node (z3) at (5,-3) {
      \includegraphics[width=0.2\linewidth]{Z3_logo.jpeg}
    };
    \node [align=left,rotate=45, scale=2, text=red!60, fill=yellow!20,draw,decorate,decoration={bumps,mirror},opacity=0] at (5,-3) {Exponentially Search ?};
  \end{tikzpicture}
\end{frame}
\begin{frame}{Exsiting Techniques to Such Constraints}
  \begin{tikzpicture}
    \node [anchor=north, anchor=west, align=left, text width = \linewidth] (text) at (-3,0) {
      Rule-based (CVC5, Z3): \textbf{Repeatly unroll} counting operators by derivation rules. For example,
      $x\in \Sigma\cdot z \wedge z\in \Sigma^*c^+$ is derived from $x\in \Sigma^*c^+$ in CVC5.
    };
    \node (cvc5) at (0,-3) {
      \includegraphics[width=0.4\linewidth]{cvc5_logo.png}
    };
    \node (z3) at (5,-3) {
      \includegraphics[width=0.2\linewidth]{Z3_logo.jpeg}
    };
    \node [align=left,rotate=45, scale=2, text=red!60, fill=yellow!20,draw,decorate,decoration={bumps,mirror}] at (5,-3) {\uppercase{Exponential ?}};
  \end{tikzpicture}
\end{frame}

\begin{frame}{Exsiting Techniques to Such Constraints}
  \begin{tikzpicture}
    \node [anchor=north, anchor=west, align=left, text width = \linewidth] (text) at (-3,0) {
      Automaton-based (Z3Str3RE, OSTRICH):\textbf{ Syntactically unwind} counting operators and then construct automata. E.g., $(\Sigma/a)^{\{1,60\}}$ is unwound to $\Sigma/a\mid \Sigma/a \Sigma/a \mid \cdots$
    };
    \node (z3) at (0,-3) {
      \includegraphics[width=0.2\linewidth]{Z3_logo.jpeg}
    };
    \node (ostrich) at (5,-3) {
      \includegraphics[width=0.3\linewidth]{ostrich_logo.jpeg}
    };
    \node [rotate=45, scale=2, text=red!60, fill=yellow!20,draw,decorate,decoration={bumps,mirror},opacity=0] at (5,-3) {STATE EXPLOSION ?};
  \end{tikzpicture}
\end{frame}
\begin{frame}{Exsiting Techniques to Such Constraints}
  \begin{tikzpicture}
    \node [anchor=north, anchor=west, align=left, text width = \linewidth] (text) at (-3,0) {
      Automaton-based (Z3Str3RE, OSTRICH):\textbf{ Syntactically unwind} counting operators and then construct automata. E.g., $(\Sigma/a)^{\{1,60\}}$ is unwound to $\Sigma/a\mid \Sigma/a \Sigma/a \mid \cdots$
    };
    \node (z3) at (0,-3) {
      \includegraphics[width=0.2\linewidth]{Z3_logo.jpeg}
    };
    \node (ostrich) at (5,-3) {
      \includegraphics[width=0.3\linewidth]{ostrich_logo.jpeg}
    };
    \node [rotate=45, scale=2, text=red!60, fill=yellow!20,draw,decorate,decoration={bumps,mirror}] at (5,-3) {STATE EXPLOSION ?};
  \end{tikzpicture}
\end{frame}

\begin{frame}{Our Techniques to Such Constraints}
  \begin{itemize}
    \item Automata with integer registers
    \item Encode counting operators by registers (no explicitly unwind)
    \item Size reduction techniques for automata
  \end{itemize}
\end{frame}

\begin{frame}{Intuition}
  \begin{tikzpicture}[anchor=west]
    \node (a_1_3) at (0, 0) {
      \begin{tikzpicture}[node distance=0.5cm, auto,semithick, font =\small, initial text=$a^{\{1,3\}}:$,
          every state/.style={inner sep=1pt, minimum size=5pt}]
        \node[state,initial] (q0) {$q_0$};
        \node[state, accepting] (q1) [right=of q0] {$q_1$};
        \node[state, accepting] (q2) [right=of q1] {$q_2$};
        \node[state, accepting] (q3) [right=of q2] {$q_3$};
        \path[->]
        (q0) edge [above] node {$a$} (q1)
        (q1) edge [above] node {$a$} (q2)
        (q2) edge [above] node {$a$} (q3);
      \end{tikzpicture}
    };
    \node (text1) at (6,0) {\textbf{Finite Automata}};
    \node [opacity = 0] (a_star) at (0,-2) {
      \begin{tikzpicture}[node distance=0.1cm, auto,semithick,  initial text=$a^{\{1,3\}}:$,
          every state/.style={inner sep=1pt, minimum size=5pt}]
        \node[state,initial,accepting] (q0) {$q_0$};
        \node (accepting_condition) [right=of q0] {$1\leq r\leq3$};
        \path[->]
        (q0) edge [loop above] node [align=center] {$r++$ \\ $a$} (q0);
      \end{tikzpicture}
    };
    \node [opacity = 0] (text2) at (6,-2) {\textbf{Extended with Registers}};
  \end{tikzpicture}
\end{frame}
\begin{frame}[fragile]{Intuition}
  \begin{tikzpicture}[anchor=west]
    \node (a_1_3) at (0, 0) {
      \begin{tikzpicture}[node distance=0.5cm, auto,semithick, initial text=$a^{\{1,3\}}:$,
          every state/.style={inner sep=1pt, minimum size=5pt}]
        \node[state,initial] (q0) {$q_0$};
        \node[state, accepting] (q1) [right=of q0] {$q_1$};
        \node[state, accepting] (q2) [right=of q1] {$q_2$};
        \node[state, accepting] (q3) [right=of q2] {$q_3$};
        \path[->]
        (q0) edge [above] node {$a$} (q1)
        (q1) edge [above] node {$a$} (q2)
        (q2) edge [above] node {$a$} (q3);
      \end{tikzpicture}
    };
    \node (text1) at (6,0) {\textbf{Finite Automata}};
    \node (a_star) at (0,-2) {
      \begin{tikzpicture}[node distance=0.1cm, auto,semithick,  initial text=$a^{\{1,3\}}:$,
          every state/.style={inner sep=1pt, minimum size=5pt}]
        \node[state,initial,accepting] (q0) {$q_0$};
        \node (accepting_condition) [right=of q0] {$1\leq r\leq3$};
        \path[->]
        (q0) edge [loop above] node [align=center] {$r++$ \\ $a$} (q0);
      \end{tikzpicture}
    };
    \node [align=center] (text2) at (6,-2.5) {\textbf{Extended with Registers}\\\textbf{(CEFA)}};

@@

\begin{frame}{$ x\in \textcolor{red}{(\Sigma / a)^{\{1,60\}}(\Sigma / b)^{\{1,60\}}(\Sigma / c)^{\{0,60\}}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120$}
  \textbf{1. Encode Counting Operators : }
  \begin{figure}
    \includegraphics[width=\linewidth]{overview_regex1.jpg}
  \end{figure}
\end{frame}
\begin{frame}{$ x\in (\Sigma / a)^{\{1,60\}}(\Sigma / b)^{\{1,60\}}(\Sigma / c)^{\{0,60\}} \wedge x\in \textcolor{red}{\Sigma^*c^+} \wedge |x| > 120$}
  \textbf{1. Basic Regex Operations : }
  \begin{figure}
    \includegraphics[width=.5\linewidth]{overview_regex2.jpg}
  \end{figure}
\end{frame}
\begin{frame}{$ x\in (\Sigma / a)^{\{1,60\}}(\Sigma / b)^{\{1,60\}}(\Sigma / c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge \textcolor{red}{|x|} > 120$}
  \textbf{1. The Pre-Image of String-Length :}
  \begin{figure}
    \includegraphics[width=.25\linewidth]{overview_length_pre.jpg}
  \end{figure}
\end{frame}

\begin{frame}{$ x\in (\Sigma / a)^{\{1,60\}}(\Sigma / b)^{\{1,60\}}(\Sigma / c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120$}
  \textbf{2. Production : }
  \begin{figure}
    \includegraphics[width=.65\linewidth]{overview_product.jpg}
  \end{figure}
\end{frame}
\begin{frame}{$ x\in (\Sigma / a)^{\{1,60\}}(\Sigma / b)^{\{1,60\}}(\Sigma / c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120$}
  \textbf{2. Abstract the Updates of Registers as Vectors : }
  \begin{figure}
    \includegraphics[width=.65\linewidth]{overview_product_vector.jpg}
  \end{figure}
\end{frame}
\begin{frame}{$ x\in (\Sigma / a)^{\{1,60\}}(\Sigma / b)^{\{1,60\}}(\Sigma / c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120$}
  \textbf{2. Size-Reduction of the Automaton : }
  \begin{figure}
    \includegraphics[width=.45\linewidth]{overview_product_vector_simplify.jpg}
  \end{figure}
\end{frame}

>>>>

\documentclass[landscape]{beamer}
\usepackage{xcolor}
\usepackage{amsmath, amsthm}
\newtheorem{benchmark}{Benchmark}
\newtheorem{environment}{Environment}
\newtheorem{distribution}{The Distribution of Counting Operators in Our Benchmark}
\usepackage{mathrsfs}
\usepackage{hyperref}
\usepackage{algpseudocode}
\usepackage{tikz}
\usetikzlibrary {decorations.pathmorphing, curvilinear, shadows,shapes.symbols, automata, positioning, shapes,arrows, matrix}
\usepackage{multicol}
\usepackage{pgfplots}
\usepackage{array}
\usepackage{colortbl}
\definecolor{grayshade}{gray}{0.9}
\usepackage{listings}
\lstdefinestyle{myjs}{
  language=C,
  basicstyle=\ttfamily,
  keywordstyle=\color{blue},
  stringstyle=\color{red},
  commentstyle=\color{green},
  backgroundcolor=\color{gray!10},
  breaklines=true,
  frame=single,
  captionpos=b
}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{graphicx}

\linespread{1.5}
\newcommand{\aut}{\mathcal{A}}
\newcommand{\myvec}[1]{\overrightarrow{#1}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\anivar}{\mathfrak{x}}
\newcommand*{\ostrichrecl}{\rm OSTRICH^{RECL}}
\newcommand*{\op}{o}
\newcommand*{\regex}{e}

@@

\title{String Constraints with Regex-Counting and
String-Length Solved More Efficiently}
\author{\textbf{Denghang Hu}, Zhilin Wu}
% \institute{}

@@

\begin{frame}{Strings are Important}
  \textbf{Strings are primitive in program languages:}
  \begin{itemize}
    \item C/C++/C\#
    \item Java
    \item JavaScript/TypeScript
    \item Python
    \item Go
  \end{itemize}
\end{frame}

\begin{frame}{Strings are Widely Used in Security-Critical Situations\footnote{Tevfik Bultan, et al.: String Analysis for Software Verification and Security.}}
  \begin{itemize}
    \item Input sanitisation, validation
    \item Quary generation for databases
    \item Data handling: XML, JSON, HTML
    \item Dynamic code generation
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Strings Are Error-Prone}
  \begin{tikzpicture}
    \node[starburst,drop shadow,fill=white,draw] at (0,0) {XSS Attack};
    \node[starburst,drop shadow,fill=white,draw] at (5,0) {ReDos Attack};
    \node[starburst,drop shadow,fill=white,draw] at (0,-3) {Broken Access Control};
    \node[starburst,drop shadow,fill=white,draw] at (5,-3) {...};
  \end{tikzpicture}
\end{frame}

\begin{frame}[fragile]{Detect Attacks by String Constraints}
  \textbf{Malicious User Input:}
  \begin{lstlisting}[style=myjs]
      <script> XSSAtack </script>
    \end{lstlisting}
  \textbf{Detect the Attack by String Constraints:}
  \begin{lstlisting}[style=myjs]
    (assert (str.contains x '<script>'))
  \end{lstlisting}
\end{frame}

\begin{frame}
  \frametitle{String Solvers}
  \begin{multicols}{2}
    \begin{itemize}
      \item ABC
      \item \textbf{CVC3/4/5}
      \item Gecode+S
      \item \textbf{OSTRICH}
      \item Stranger
      \item S3/p/\#
      \item Sloth
      \item SLENT
      \item TRAU/+
      \item Woorpje
      \item \textbf{Z3str2/3/4/RE/Seq}
      \item ...
    \end{itemize}
  \end{multicols}
\end{frame}

\begin{frame}{Motivation Example}
  \textbf{CVC5 and Z3 Cannot Solve:}
  \begin{tikzpicture}
    \node (formula) at (0,0) {
    $
      x\in (\Sigma \backslash a)^{\textcolor{red}{\{1,60\}}}(\Sigma \backslash b)^{\textcolor{red}{\{1,60\}}}(\Sigma \backslash c)^{\textcolor{red}{\{0,60\}}} \wedge x\in \Sigma^*c^+ \wedge \textcolor{red}{|x|} > 120
    $
    };
    \node [rotate=45, scale=2, text=red!90, fill=yellow!20,draw,decorate,decoration={bumps,mirror}, opacity=0] at (1,0) {300s TIMEOUT};
  \end{tikzpicture}
\end{frame}
\begin{frame}{Motivation Example}
  \textbf{CVC5 and Z3 Cannot Solve:}
  \begin{tikzpicture}
    \node (formula) at (0,0) {
    $
      x\in (\Sigma \backslash a)^{\textcolor{red}{\{1,60\}}}(\Sigma \backslash b)^{\textcolor{red}{\{1,60\}}}(\Sigma \backslash c)^{\textcolor{red}{\{0,60\}}} \wedge x\in \Sigma^*c^+ \wedge \textcolor{red}{|x|} > 120
    $
    };
    \node [rotate=45, scale=2, text=red!90, fill=yellow!20,draw,decorate,decoration={bumps,mirror}] at (1,0) {300s TIMEOUT};
  \end{tikzpicture}
\end{frame}

\begin{frame}[fragile]
  \frametitle{However ...}
  \textbf{Regex-Countings are Widely Used}
  \begin{table}
    \centering
    \begin{tabular}{l l l S[table-format=1.2]}
      \toprule
      \textbf{Rank} & \textbf{Type}  & \textbf{Example} & \textbf{\% Projects} \\
      \midrule
      1             & $\cdot\{1,\}$  & $z^+$            & 73.2                 \\
      3             & $\cdot\{0,\}$  & $z^*$            & 66.8                 \\
      18            & $\cdot\{n\}$   & $z\{8\}$         & 20.7                 \\
      20            & $\cdot\{n,m\}$ & $z\{8,9\}$       & 14.5                 \\
      \bottomrule
    \end{tabular}
    \caption{The Rank and Percentage of Regex-Countings in Python \footnote{Chapman,C. et al: Exploring regular expression usage and context in python}}
  \end{table}

@@

% Technical details : (8min)
% 1 What is Regex-Counting
% 2 normal ways (z3, cvc5, trau)
% 3 our ways
%   1 An example (5-7 pages)
%   2 Decisino procedure 1 pages
\section{Our Approach}
\begin{frame}{The Problem}
  Syntax of \textbf{RE}gex-\textbf{C}ounting \textbf{L}ogic (\textbf{RECL}):
  \begin{figure}[h]
    \centering
    \resizebox{1\linewidth}{!}{
      $
        \begin{array}{l l l l}
          \varphi & ::= & x\in \regex \mid t_1\  \op\ t_2 \mid  \varphi \wedge \varphi                                                                                         & \mbox{formulas}      \\
          \regex  & ::= & \emptyset \mid \epsilon \mid a \mid \regex\cdot \regex \mid \regex+\regex \mid \regex^* \mid \regex \cap \regex \mid                                 &                      \\
                  &     & \overline{\regex} \mid \regex \setminus \regex \mid {\textcolor{red!90}{\regex^{\{m,n\}}}} \mid {\textcolor{red!90}{\regex^{\{m,\infty\}}}} \mid (e) & \mbox{regexes}       \\
          t       & ::= & n \mid \anivar \mid  {\textcolor{red!90}{|x|}} \mid t - t \mid t + t                                                                                 & \mbox{integer terms}
        \end{array}
      $
    }
  \end{figure}
\end{frame}
\begin{frame}{Motivation Example}
  \begin{tikzpicture}
    \node (placeholder) at (0,0) {
    $
      x\in (\Sigma \backslash a)^{\textcolor{red}{\{1,60\}}}(\Sigma \backslash b)^{\textcolor{red}{\{1,60\}}}(\Sigma \backslash c)^{\textcolor{red}{\{0,60\}}} \wedge x\in \Sigma^*c^+ \wedge \textcolor{red}{|x|} > 120
    $
    };
    \node [rotate=45, scale=2, text=red!90, fill=yellow!20,draw,decorate,decoration={bumps,mirror}, opacity=0] at (1,0) {300s TIMEOUT};
  \end{tikzpicture}
\end{frame}

\begin{frame}[fragile]{Exsiting Techniques to Solve Such Constraints}
  \begin{minipage}{0.48\linewidth}
    \begin{tikzpicture}
      \node [anchor=west, align=left, text width = .9\linewidth] (text) at (0,-2) {
        Rule-based (CVC5, Z3): \\ \textbf{Repeatly unwind} counting operators by derivation rules.
      };
      \node [anchor=west, align=left] (cvc5) at (0,-4) {
        \includegraphics[width=0.4\linewidth]{cvc5_logo.png}
      };
      \node [anchor=west, align=left] (z3) at (3,-4) {
        \includegraphics[width=0.2\linewidth]{Z3_logo.jpeg}
      };
      \node [anchor=west, align=left] (example) at (0,-5.5) {$a^{\{1,3\}}: a, aa, aaa$};
      \node [anchor=west, align=left,rotate=45, scale=1.5, text=red!90, fill=yellow!20,draw,decorate,decoration={bumps,mirror}, opacity = 0] at (0,-5.5) {Exponential Search Space};
    \end{tikzpicture}
  \end{minipage}
  \begin{minipage}{0.48\linewidth}
    \begin{tikzpicture}
      \node [anchor=west, align=left, text width = \linewidth] (text) at (0,-2) {
        Automaton-based (Z3Str3RE, OSTRICH):\textbf{Unwind} counting operators before constructing automata.
      };
      \node [anchor = west, align=center] (z3) at (3,-4) {
        \includegraphics[width=0.25\linewidth]{ostrich_logo.jpeg}
      };
      \node [anchor = west, align=left, rotate=45, scale=1.5, text=red!90, fill=yellow!20,draw,decorate,decoration={bumps,mirror}, opacity = 0] at (0,-4) {State Explosion};
      \node [anchor=west, align=left] (example) at (0,-5.5) {
        \begin{tikzpicture}[node distance=0.5cm, auto,semithick, initial text=$a^{\{1,3\}}:$,
            every state/.style={inner sep=1pt, minimum size=5pt}]
          \node[state,initial] (q0) {$q_0$};
          \node[state, accepting] (q1) [right=of q0] {$q_1$};
          \node[state, accepting] (q2) [right=of q1] {$q_2$};
          \node[state, accepting] (q3) [right=of q2] {$q_3$};
          \path[->]
          (q0) edge [above] node {$a$} (q1)
          (q1) edge [above] node {$a$} (q2)
          (q2) edge [above] node {$a$} (q3);
        \end{tikzpicture}
      };
    \end{tikzpicture}
  \end{minipage}
\begin{frame}[fragile]{Exsiting Techniques to Solve Such Constraints}
  \begin{minipage}{0.48\linewidth}
    \begin{tikzpicture}
      \node [anchor=west, align=left, text width = .9\linewidth] (text) at (0,-2) {
        Rule-based (CVC5, Z3): \\ \textbf{Repeatly unwind} counting operators by derivation rules.
      };
      \node [anchor=west, align=left] (cvc5) at (0,-4) {
        \includegraphics[width=0.4\linewidth]{cvc5_logo.png}
      };
      \node [anchor=west, align=left] (z3) at (3,-4) {
        \includegraphics[width=0.2\linewidth]{Z3_logo.jpeg}
      };
      \node [anchor=west, align=left] (example) at (0,-5.5) {$a^{\{1,3\}}: a, aa, aaa$};
      \node [anchor=west, align=left,rotate=45, scale=1.5, text=red!90, fill=yellow!20,draw,decorate,decoration={bumps,mirror}] at (0,-5.5) {Exponential Search Space};
    \end{tikzpicture}
  \end{minipage}
  \begin{minipage}{0.48\linewidth}
    \begin{tikzpicture}
      \node [anchor=west, align=left, text width = \linewidth] (text) at (0,-2) {
        Automaton-based (Z3Str3RE, OSTRICH):\textbf{Unwind} counting operators before constructing automata.
      };
      \node [anchor = west, align=center] (z3) at (3,-4) {
        \includegraphics[width=0.25\linewidth]{ostrich_logo.jpeg}
      };
      \node [anchor = west, align=left, rotate=45, scale=1.5, text=red!90, fill=yellow!20,draw,decorate,decoration={bumps,mirror}] at (0,-4) {State Explosion};
      \node [anchor=west, align=left] (example) at (0,-5.5) {
        \begin{tikzpicture}[node distance=0.5cm, auto,semithick, initial text=$a^{\{1,3\}}:$,
            every state/.style={inner sep=1pt, minimum size=5pt}]
          \node[state,initial] (q0) {$q_0$};
          \node[state, accepting] (q1) [right=of q0] {$q_1$};
          \node[state, accepting] (q2) [right=of q1] {$q_2$};
          \node[state, accepting] (q3) [right=of q2] {$q_3$};
          \path[->]
          (q0) edge [above] node {$a$} (q1)
          (q1) edge [above] node {$a$} (q2)
          (q2) edge [above] node {$a$} (q3);
        \end{tikzpicture}
      };
    \end{tikzpicture}
  \end{minipage}

% \begin{frame}{Our Techniques to Such Constraints}
%   \begin{itemize}
%     \item Automata with integer registers
%     \item Encode counting operators by registers (no explicitly unwind)
%     \item Size reduction techniques for automata
%   \end{itemize}
% \end{frame}

\begin{frame}[fragile]{The Main Idea of Our Approach}
  \linespread{0.9}
  \begin{tikzpicture}[anchor=west]
    \node (a_1_3) at (0, 0) {
      \begin{tikzpicture}[node distance=0.5cm, auto,semithick, initial text=$a^{\{1,3\}}:$,
          every state/.style={inner sep=1pt, minimum size=5pt}]
        \node[state,initial] (q0) {$q_0$};
        \node[state, accepting] (q1) [right=of q0] {$q_1$};
        \node[state, accepting] (q2) [right=of q1] {$q_2$};
        \node[state, accepting] (q3) [right=of q2] {$q_3$};
        \path[->]
        (q0) edge [above] node {$a$} (q1)
        (q1) edge [above] node {$a$} (q2)
        (q2) edge [above] node {$a$} (q3);
      \end{tikzpicture}
    };
    \node (text1) at (6,0) {\textbf{Finite Automata}};
    \node (a_1_3_cefa) at (0,-1.5) {
      \begin{tikzpicture}[node distance=0.1cm, auto,semithick,  initial text=$a^{\{1,3\}}:$,
          every state/.style={inner sep=1pt, minimum size=5pt}]
        \node[state,initial,accepting] (q0) {$q_0$};
        \node (accepting_condition) [right=of q0] {$\textcolor{red!90}{1\leq r\leq3}$};
        \path[->]
        (q0) edge [loop above] node [align=center] {$\textcolor{red!90}{r++}$ \\ $a$} (q0);
      \end{tikzpicture}
    };
    \node [align=center] (text2) at (5,-3.25) {\textbf{Cost-Enriched Finite Automata}\\\textbf{(CEFA)}};
    \node (a_len) at (0, -4) {
      \begin{tikzpicture}[node distance=0.1cm, auto,semithick,  initial text=$|x|:$,
          every state/.style={inner sep=1pt, minimum size=5pt}]
        \node[state,initial,accepting] (q0) {$q_0$};
        \node (accepting_condition) [right=of q0] {$\textcolor{red!90}{true}$};
        \path[->]
        (q0) edge [loop above] node [align=center] {$\textcolor{red!90}{r++}$ \\ $\Sigma$} (q0);
      \end{tikzpicture}
    };

@@

\begin{frame}{$ x\in \textcolor{red!90}{(\Sigma \backslash a)^{\{1,60\}}(\Sigma \backslash b)^{\{1,60\}}(\Sigma \backslash c)^{\{0,60\}}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120$}
  \textbf{1. Encode Counting Operators and Lengths by CEFAs }
  \begin{figure}
    \includegraphics[width=\linewidth]{overview_regex1.jpg}
  \end{figure}
\end{frame}
\begin{frame}{$ x\in (\Sigma \backslash a)^{\{1,60\}}(\Sigma \backslash b)^{\{1,60\}}(\Sigma \backslash c)^{\{0,60\}} \wedge x\in \textcolor{red!90}{\Sigma^*c^+} \wedge |x| > 120$}
  \textbf{1. Encode Counting Operators and Lengths by CEFAs }
  \begin{figure}
    \includegraphics[width=.5\linewidth]{overview_regex2.jpg}
  \end{figure}
\end{frame}
\begin{frame}{$ x\in (\Sigma \backslash a)^{\{1,60\}}(\Sigma \backslash b)^{\{1,60\}}(\Sigma \backslash c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge \textcolor{red!90}{|x|} > 120$}
  \textbf{1. Encode Counting Operators and Lengths by CEFAs}
  \begin{figure}
    \includegraphics[width=.25\linewidth]{overview_length_pre.jpg}
  \end{figure}
\end{frame}

\begin{frame}{$ x\in (\Sigma \backslash a)^{\{1,60\}}(\Sigma \backslash b)^{\{1,60\}}(\Sigma \backslash c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge |x| > 120$}
  \textbf{2. Compute the Product of CEFAs }
  \begin{figure}
    \includegraphics[width=.65\linewidth]{overview_product.jpg}
  \end{figure}
\end{frame}
\begin{frame}{$ x\in (\Sigma \backslash a)^{\{1,60\}}(\Sigma \backslash b)^{\{1,60\}}(\Sigma \backslash c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge \textcolor{red}{|x| > 120}$}
  \textbf{2. Compute the Product of CEFAs }
  \begin{tikzpicture}
    \node (product) at (0,0) {
      \includegraphics[width=.65\linewidth]{overview_product.jpg}
    };
    \node (lia) at (6,0) {
      $\textcolor{red}{r_4 > 120}$
    };
  \end{tikzpicture}
\end{frame}
\begin{frame}{$ x\in (\Sigma \backslash a)^{\{1,60\}}(\Sigma \backslash b)^{\{1,60\}}(\Sigma \backslash c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge \textcolor{red}{|x| > 120}$}
  \textbf{2. Compute the Product of CEFAs }
  \begin{tikzpicture}
    \node (product) at (0,0) {
      \includegraphics[width=.65\linewidth]{overview_product.jpg}
    };
    \node (lia) at (6,0) {
      $\textcolor{red}{r_4 > 120}$
    };
    \node (nonempty) [scale=1.3, text=blue!60, fill=yellow!20,draw,decorate,decoration={bumps,mirror}] at (2, 0) {The Nonemptiness of CEFA w.r.t LIA Formulas};
  \end{tikzpicture}
\end{frame}
\begin{frame}{$ x\in (\Sigma \backslash a)^{\{1,60\}}(\Sigma \backslash b)^{\{1,60\}}(\Sigma \backslash c)^{\{0,60\}} \wedge x\in \Sigma^*c^+ \wedge \textcolor{red}{|x| > 120}$}
  \textbf{2. Compute the Product of CEFAs }
  \begin{tikzpicture}
    \node (product) at (0,0) {
      \includegraphics[width=.65\linewidth]{overview_product.jpg}
    };
    \node (lia) at (6,0) {
      $\textcolor{red}{r_4 > 120}$
    };
    \node (nonempty) [scale=1.3, text=blue!60, fill=yellow!20,draw,decorate,decoration={bumps,mirror}] at (2, 0) {The Nonemptiness of CEFA w.r.t LIA Formulas};
    \node (satisfy) [scale=1.3, text=red!60, fill=yellow!20,draw,decorate,decoration={bumps,mirror}] at (2, -2) {The Satisfiability of LIA Formulas};
    \draw [->, line width=4pt, orange!100, -triangle 90] (nonempty) -- (satisfy);
  \end{tikzpicture}
\end{frame}
